---
title: "Happy Valentines Day via R"
author: "John Minter"
date: "2018-02-14"
categories:
  - R
tags:
  - R Markdown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, message = FALSE)
```

Today we have something completely different. We will construct
a Valentine using R. The idea came from the **#rstats**
community.

First we need a Valentine function. Let's build one and then
create a dataframe to plot. The function code comes from Daniel
Marcelino via
[Mara Averick](https://twitter.com/dataandme/status/963745759098228737).

```{r, buildValentine, echo=TRUE}

dat <- data.frame(t=seq(0, 2*pi, by=0.1))
xhrt <- function(t){16*sin(t)^3}
yhrt <- function(t){13*cos(t)-5*cos(2*t)-2*cos(3*t)-cos(4*5)}
dat$y=yhrt(dat$t)
dat$x=xhrt(dat$t)

```

Now, plot our Valentine using `ggplot2`. It took me a while to
figure out how to use `geom_polygon()`. I like this better than
base graphics. I subsequently discovered that
[David Robinson](https://twitter.com/drob/status/963902212496818177)
had come up with a similar aporach. I added his call to `coord_fixed()`
and kept `theme_void` where he used `theme_minimal()`. 


```{r plotValentine, fig.width=6}
library(ggplot2)
plt <- ggplot(dat, aes(x=x, y=y)) +
  geom_polygon(color="darkred", fill="darkred") +
  coord_fixed() +
  theme_void()

print(plt)
```

Ideas from the [rstats](https://twitter.com/hashtag/rstats)
community help each of us to refine ideas.
